---
title: "Exercise1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mosaic)
library(knitr)
milk = read.csv("./milk.csv")
greenbuildings = read.csv("./greenbuildings.csv")
ABIA = read.csv("./ABIA.csv")
creatinine = read.csv("./creatinine.csv")
```

## ABIA

```{r}
temp3 = ABIA %>%
  group_by(UniqueCarrier, Cancelled) %>%
  summarise(cancel_sum = n())

ggplot(temp3, aes(x=reorder(UniqueCarrier, -cancel_sum), y = cancel_sum)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Carrier", y = "Cancelled Flights", title = "Cancelled Flights by Carrier")

# Histogram showing proportion of green rating by rent faceted
ggplot(filter(ABIA, (UniqueCarrier == "WN" | UniqueCarrier == "CO" | UniqueCarrier == "AA") & CancellationCode != ""), aes(x = factor(CancellationCode), fill = factor(CancellationCode))) +
  theme_bw() +
  facet_wrap(~ UniqueCarrier, ncol = 1) +
  geom_bar() +
  labs(y = "Cancelled Flights", x = "Cancellation Code", title = "Top 3 Carriers in terms of Cancellations") +
  facet_grid(. ~ UniqueCarrier, labeller = labeller(UniqueCarrier = c(AA = "American Airlines", CO = "Continental Airlines", WN = "Southwest Airlines"))) +
  scale_fill_discrete(name = "Cancellation Codes", labels = c("Carrier", "Weather", "NAS"))
```

## Regression Practice

```{r}
ggplot(creatinine, aes(x=age, y=creatclear)) + 
  geom_point() +
  geom_smooth(method="lm") + 
  labs(
    x = "age (years)",
    y = "creatinine clearance rate (mL/minute)",
    title = "Creatinine Clearance Rate vs Age"
  )
reg = lm(creatclear ~ age, data=creatinine)
coef(reg) ## just coefficients

```
Using the linear regression model for creatinine clearance rate as a function of age, we obtain the following equation: 
Y(creatinine clearance rate, mL/min) = -0.620*X(age, years) + 147.813(mL/min)

*What creatinine clearance rate should we expect, on average, for a 55-year-old?*
```{r}
-0.62*55 + 147.813
```
By using the regression model, we can expect an average creatinine clearance rate for a 55 year old to be 113.713mL/min. 

*How does creatinine clearance rate change with age? (This should be a number with units mL/min per year).*

Looking at the slope of the linear model, creatinine clearance rate changes by -0.620mL/min per year.

*Whose creatinine clearance rate is healthier (higher) for their age: a 40-year-old with a rate of 135, or a 60-year-old with a rate of 112?*

Using the model, we can determine health by looking at the percent difference between actual and expected creatinine clearance rates for each age. 
```{r}
-0.62*40 + 147.813 #Expected 40 year old
-0.62*60 + 147.813 #Expected 60 year old
```
```{r}
#The difference for the 40 year old is:
135 - 123.013
#The difference for the 60 year old is:
112 - 110.613
#Percent difference for each:
100 * 11.987/((135 + 123.013)/2)
100 * 1.387/((112 + 110.613)/2) 

```
The 40 year old's creatinine clearance rate is 9.29% higher than expected for their age, while the 60 year old's rate is only 1.25% higher. From this, we can determine that the 40 year old has a healthier creatinine clearance rate for their age. 

## Green Buildings

According to the report by the total Excel guru, the reason that she recommends builing a green building is because of the increase in tenant rent which would result in greater profit. However, through our research on this dataset, we have discovered a confounding variable as well as inconsistencies in the dataset that makes her claim less credible.

First, we would like to point out that there is a large disparity in the number of green vs non-green buildings in the dataset.

```{r}
# Disparity between green housing and non green housing
ggplot(greenbuildings, aes(x = green_rating == 1, fill=green_rating)) +
  theme_classic() +
  geom_bar(show.legend = FALSE) +
  labs(y = "Buildings", x = "Green Rating", title = "Green vs Non-Green Housing")

# Add proportion
greenprop <- prop.table(table(greenbuildings$green_rating))

print(kable(greenprop, format = "markdown", col.names = c("Green Rating", "Frequency")))
```

As shown above, over 90% of the dataset is made out of non-green buildings, so there might not be an even comparison between the two. In addition, the possible confounding variable we discovered was the age of the buildings.

```{r}
# Histogram showing proportion of green rating by age
ggplot(greenbuildings, aes(x = age, fill = green_rating == 1)) +
  theme_bw() +
  geom_density(alpha = 0.5) +
  labs(x = "Age of Building", y = "Percentage of Buildings") +
  scale_fill_discrete(name = "Green Rating")
```

The age category potentially affects Rent, as newer buildings tend to be more expensive due to having modern features, and affects Green Rating, as newer buildings are more likely to have green certifications due to the facts that builders are currently more environmentally conscious and these green certifications are only a recent development (post 1992 and 1993 for Energystar and LEED respectively). We believe that the dataset is distorted by the abundance of older buildings; a housing developer would find a dataset of recent buildings to be more relevant. A better solution would be to look at buildings less than 10 years old, as shown in the plot below. This analysis indicates that recently built green buildings in fact have a lower median Rent by about $2.5.

```{r}
ggplot(filter(greenbuildings, age < 10 ), aes(fill = factor(green_rating), x = factor(green_rating), y = Rent)) +
  labs(x = "Green Rating", y = "Rent", title = "Rent vs Green Rating for Buildings < 10 Years")+
  geom_boxplot()
test = filter(greenbuildings, age < 10) %>%
  group_by(green_rating) %>%
  summarise(median_rent = median(Rent))
print(kable(test, format = "markdown", col.names = c("Green Rating", "Median Rent")))
```

Finally, we noticed that a building has a green rating if it has either the Energystar or LEED certification, both of which use different criteria for qualification. Therefore, some buildings in the dataset are more green than others which causes some inconsistency in the data provided. For example, the median rent of LEED certified buildings are higher than that of non-LEED certified buildings by \$4, while the median rent of Energy Star certified buildings is less than non-Energy Star certified buildings by \$1.74.

```{r}
ggplot(greenbuildings, aes(x = factor(LEED), y = Rent, fill = factor(LEED))) +
  geom_boxplot()

test1 = filter(greenbuildings, age < 10) %>%
  group_by(LEED) %>%
  summarise(median_rent = median(Rent))

print(kable(test1, format = "markdown", col.names = c("LEED", "Median Rent")))

ggplot(greenbuildings, aes(x = factor(Energystar), y = Rent, fill = factor(Energystar))) +
  geom_boxplot()

test2 = filter(greenbuildings, age < 10) %>%
  group_by(Energystar) %>%
  summarise(median_rent = median(Rent))

print(kable(test2, format = "markdown", col.names = c("LEED", "Median Rent")))
```

In light of the above findings, we find it hard to recommend building the green building solely based on rent increase due to green certification.

## Milk Report
### The Approach: 

Using the guidelines from step 1 on the milk assignment, we used the variables N: net profit, Q: quantity sold, and c: unit cost to form the equation that follows.
N = QP - Qc
which simplifies to 
N = Q(P-C)
P and Q are coupled since the price of a product affects the amount sold. As such, Q can be expressed as a function of P as follows:
N = f(P) * (P - C)

We used a scatter plot to illustrate the relationship between P and Q. 
```{r}
plot(sales ~ price, data=milk)
```

Since the distribution of the points closely resemble that of an exponential function, we plotted another scatter plot comparing log(P) and log(Q) to confirm our hypothesis and linearize the data.
```{r}
plot(log(sales) ~ log(price), data=milk)

abline(lm(log(sales) ~ log(price), data=milk))
```

The data illustrates a clear linear relationship between log(P) and log(Q). We created a regression model and identified the coefficients to find the parameters Beta 1 and Beta 0. 
```{r}
lm_ped = lm(log(sales) ~ log(price), data = milk)
coef(lm_ped)
```
This can be illustrated as the following regression model:
log(Q) = 4.72 - 1.62log(P)
Q = e^(4.72) * P^(-1.62)
We can combine both the first and second equations to illustrate N only in terms of P and c:
N = (P-c) * 110 * P^(-1.62)
With this equation, for any given unit cost c (consider c = 1), we can calculate the max N by plotting a graph of the equation and visually identifying the maximum.
```{r}
curve((x-1)*110*x^(-1.62), from=2, to=3)
```

From this graph, we can identify the max N as $2.61 for a given c of \$1.